Interpretable Machine Learning

### 2019-01-08 chunks/tools.Rmd
starts contructing wine analysis

IF $90m^2\

@@

@@

## Example-based methods

@@

## Example-focused methods
```{r, echo=FALSE}
knitr::include_graphics("../images/data-box.png")
```

@@

>>>>

IF $90m^2\leq \text{size} < 110m^2$  AND location $=$ "good" THEN rent is between 1540 and 1890 EUR

@@

TODO: Example for CNNs

TODO: Example for text (RNNs and attention?)

@@

## Model-agnostic Methods

TODO: PDP gif

TODO: Feature importance figure

## Model-agnostic methods: Global Surrogate {.center data-background=../images/global-surrogate.png data-background-size=contain}

## Model-agnostic methods: Local Surrogate {.center data-background=../images/local-surrogate.png data-background-size=contain}

## Example-based Methods

@@

## Example-focused Methods
```{r, echo=FALSE}
knitr::include_graphics("../images/data-box.png")
```

@@

## Example-focused Methods

TODO: Graphic for counterfactuals

## Example-focused Methods

TODO: Graphic for prototypes
